\begin{thebibliography}{00}

\bibitem{Cassandra}
The apache cassandra project.
\newblock http://cassandra.apache.org/.

\bibitem{Riak}
basho.
\newblock \url{http://basho.com/products/riak-s2/}.
\newblock [Online; accessed 30-October-2018].

\bibitem{cockroachDB}
cockroachdb.
\newblock https://www.cockroachlabs.com/.

\bibitem{DBEnginesCassandra}
Db-engines: Cassandra system properties.
\newblock \url{https://db-engines.com/en/system/Cassandra}.
\newblock [Online; accessed 14-March-2020].

\bibitem{MininetWebsite}
Mininet.
\newblock \url{http://mininet.org/}.
\newblock [Online; accessed 14-March-2020].

\bibitem{ABD96}
H.~Attiya, A.~Bar-Noy, and D.~Dolev,
``Sharing memory robustly in message passing systems,''
Journal of the ACM, 42(1):124--142, 1996.

\bibitem{pbs-vldb2012}
Peter Bailis, Shivaram Venkataraman, Michael~J. Franklin, Joseph~M.
  Hellerstein, and Ion Stoica,
``Probabilistically bounded staleness for practical partial quorums,''
PVLDB, 5(8):776--787, 2012.

\bibitem{DepSky13}
A.~Bessani, M.~Correia, B.~Quaresma, F.~Andr{\'e}, and P.~Sousa,
``{D}ep{S}ky: dependable and secure storage in a cloud-of-clouds,''
ACM {T}ransactions on Storage, 9(4):1--33, 2013.

\bibitem{CadambeLMM17}
Viveck~R. Cadambe, Nancy~A. Lynch, Muriel M{\'{e}}dard, and Peter~M. Musial,
``A coded shared atomic memory algorithm for message passing
  architectures,''
Distributed Computing, 30(1):49--73, 2017.

\bibitem{cadambe2016information}
Viveck~R Cadambe, Zhiying Wang, and Nancy Lynch,
``Information-theoretic lower bounds on the storage cost of shared
  memory emulation,''
in Proceedings of the 2016 ACM Symposium on Principles of
  Distributed Computing, pages 305--313, 2016.

\bibitem{GIZA2017}
Yu~Lin~Chen Chen, Shuai Mu, and Jinyang Li,
``Giza: Erasure coding objects across global data centers,''
in Proceedings of the 2017 USENIX Annual Technical Conference
  (USENIX ATC ’17), pages 539--551, 2017.

\bibitem{YCSB:2010}
Brian~F. Cooper, Adam Silberstein, Erwin Tam, Raghu Ramakrishnan, and Russell Sears,
``Benchmarking cloud serving systems with YCSB,''
in Proceedings of the 1st ACM Symposium on Cloud Computing,
  SoCC '10, pages 143--154, 2010.

\bibitem{DGL08}
Partha Dutta, Rachid Guerraoui, and Ron~R. Levy.
``Optimistic erasure-coded distributed storage,''
in Proceedings of the 22nd international symposium on
  Distributed Computing (DISC), pages 182--196, Berlin, Heidelberg, 2008.

\bibitem{Spanner}
Corbett et~al, ``Spanner: Google's globally-distributed database,''
in Proceedings of the 10th USENIX Conference on Operating
  Systems Design and Implementation, OSDI'12, pages 251--264, 
  USA, 2012.

\bibitem{Tseng_Cass}
Guo-Shu~Gau et~al,
``Practical experience report: Cassandra+: Trading-off consistency,
  latency, and fault-tolerance in cassandra,''
in 22nd International Conference on Distributed Computing and
  Networking (ICDCN),   2021.

\bibitem{LDS2017}
Kishori M.~Konwar et~al,
``A layered architecture for erasure-coded consistent distributed
  storage,''
in Proceedings of the {ACM} Symposium on Principles of
  Distributed Computing, {PODC} 2017, 
  pages 63--72, 2017.

\bibitem{SODA2016}
Konwar et~al,
``Storage-optimized data-atomic algorithms for handling erasures and
  errors in distributed storage systems,''
in 30th IEEE International Parallel \& Distributed Processing
  Symposium (IPDPS), 2016.

\bibitem{herlihy1990linearizability}
Maurice~P Herlihy and Jeannette~M Wing,
``Linearizability: A correctness condition for concurrent objects,''
in ACM Transactions on Programming Languages and Systems (TOPLAS),
  12(3):463--492, 1990.

\bibitem{HuaSimXu_etal_azure}
C.~Huang, H.~Simitci, Y.~Xu, A.~Ogus, B.~Calder, P.~Gopalan, J.~Li, and
  S.~Yekhanin,
``Erasure coding in windows azure storage,''
in Proc. USENIX Annual Technical Conference, pages 15--26,
  2012.

\bibitem{verapless_book}
W.~C. Huffman and V.~Pless,
``Fundamentals of error-correcting codes,''
Cambridge University Press, 2003.

\bibitem{lamport}
Leslie Lamport,
``Time, clocks, and the ordering of events in a distributed system,''
Commun. ACM, 21(7):558--565, July 1978.

\bibitem{paxos}
Leslie Lamport,
``The part-time parliament,''
in ACM Trans. Comput. Syst., 16(2):133--169, May 1998.

\bibitem{Lynch1996}
N.A. Lynch,
``Distributed Algorithms,''
Morgan Kaufmann Publishers, 1996.

\bibitem{NicolaouC0KML19}
Nicolas~C. Nicolaou, Viveck~R. Cadambe, N.~Prakash, Kishori~M. Konwar, Muriel
  M{\'{e}}dard, and Nancy~A. Lynch,
``ARES: adaptive, reconfigurable, erasure coded, atomic storage,''
in 39th {IEEE} International Conference on Distributed Computing
  Systems, {ICDCS} 2019, Dallas, TX, USA, July 7-10, 2019, pages 2195--2205.
  {IEEE}, 2019.

\bibitem{rashmi_fast15}
K.~V. Rashmi, P.~Nakkiran, J.~Wang, N.~B. Shah, and K.~Ramchandran,
``Having your cake and eating it too: Jointly optimal erasure codes for
  i/o, storage, and network-bandwidth,''
in 13th USENIX Conference on File and Storage Technologies
  (FAST), pages 81--94, 2015.

\bibitem{rashmi2016ec}
KV~Rashmi, Mosharaf Chowdhury, Jack Kosaian, Ion Stoica, and Kannan
  Ramchandran,
``Ec-cache: Load-balanced, low-latency cluster caching with online
  erasure coding,''
in OSDI, pages 401--417, 2016.

\bibitem{sathiamoorthy}
M.~Sathiamoorthy, M.~Asteris, D.~Papailiopoulos, A.~G. Dimakis, R.~Vadali,
  S.~Chen, and D.~Borthakur,
``XORing elephants: novel erasure codes for big data,''
in Proceedings of the 39th international conference on Very
  Large Data Bases, pages 325--336, 2013.

\bibitem{Dynamo}
Alexander Shraer, Jean-Philippe Martin, Dahlia Malkhi, and Idit Keidar,
``Data-centric reconfiguration with network-attached disks, ''
 in Proceeding of the 4th Int'l Workshop on Large Scale
  Distributed Systems and Middleware (LADIS 2010), 2004.

\bibitem{SCCK15}
Alexander Spiegelman, Yuval Cassuto, Gregory Chockler and Idit Keidar.
``Space bounds for reliable storage: Fundamental limits of coding,''
Technical report, arXiv:1507.05169v1, 2015.

\bibitem{tamo2014family}
Itzhak Tamo and Alexander Barg,
``A family of optimal locally recoverable codes,''
IEEE Transactions on Information Theory, 60(8):4661--4676, 2014.

\bibitem{wang2018multi}
Zhiying Wang and Viveck~R Cadambe,
``Multi-version coding—an information-theoretic perspective of
  consistent distributed storage,'' in  IEEE Transactions on Information Theory, 64(6):4540--4561,
  2018.

\bibitem{Cocytus2016}
Heng Zhang, Mingkai Dong, and Haibo Chen,
``Efficient and available in-memory KV-store with hybrid erasure coding
  and replication,'' in 14th {USENIX} Conference on File and Storage Technologies
  ({FAST} 16), pages 167--180, 2016.

\end{thebibliography}
